\Rpackage{MSnbase} input/output capabilities

### 2013-01-15 inst/doc/MSnbase-io/MSnbase-io.Rnw
knity 1.0 compatibility
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@72561 bc3139a8-67e5-0310-9ffc-ced21a209358

%\VignetteIndexEntry{MSnbase IO capabilities}
%\VignetteKeywords{Mass Spectrometry, Proteomics, Infrastructure }
%\VignettePackage{MSnbase-io}
\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,shadows,fit}
\usepackage[nogin]{Sweave}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}

@@

<<knitr, include=FALSE, cache=FALSE>>=
library(knitr)
opts_chunk$set(fig.align = 'center', 
               fig.show = 'hold', 
               par = TRUE,
               prompt = TRUE,
               comment = NA)
options(replace.assign = TRUE, 
        width = 70)
knit_hooks$set(par = function(before, options, envir) {
  if (before && options$fig.show != 'none') 
    par(mar = c(4,4,.1,.1),
        cex.lab = .95,
        cex.axis = .9,
        mgp = c(2,.7,0),
        tcl = -.3)
})
@

@@

%% <<label=sessioninfo,results=tex,echo=FALSE,cache=FALSE>>=
%% toLatex(sessionInfo())
%% @

>>>>

%\VignetteIndexEntry{MSnbase IO capabilities}
%\VignetteKeywords{Mass Spectrometry, Proteomics, Infrastructure }
%\VignettePackage{MSnbase-io}
\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,shadows,fit}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}

@@

<<knitr, include=FALSE, cache=FALSE>>=
library(knitr)
opts_chunk$set(fig.align = 'center', 
               fig.show = 'hold', 
               par = TRUE,
               prompt = TRUE,
               comment = NA)
options(replace.assign = TRUE, 
        width = 70)
@

@@

%% <<label=sessioninfo,results='asis',echo=FALSE,cache=FALSE>>=
%% toLatex(sessionInfo())
%% @
